BETTING AND BELIEF: PREDICTION MARKETS AND ATTRIBUTION OF CLIMATE CHANGE

### 2016-06-28 README.Rmd
Made a few wordsmithing edits:
Added a direct link to the ODD at the top of the MODEL DESIGN section, and added a mention that the model code is also available at the project web site.

Fixed an erroneous description of risk.tak in the DISCUSSION section.

Minor wordsmithing to save a line here and there, where there was only one word in the last line of a paragraph, to keep the length to 12 pages.

The paper can be downloaded here: [http://arxiv.org/abs/1603.08961](http://arxiv.org/abs/1603.08961)

>>>>

The paper can be downloaded here: [http://arxiv.org/abs/1603.08961](http://arxiv.org/abs/1603.08961) and the ODD specification for the agent-based prediction-market model can be found here: [https://github.com/JohnNay/predMarket/blob/master/odd.pdf](https://github.com/JohnNay/predMarket/blob/master/odd.pdf)

### 2016-06-28 prediction_market_wsc.Rnw
Made a few wordsmithing edits:
Added a direct link to the ODD at the top of the MODEL DESIGN section, and added a mention that the model code is also available at the project web site.

Fixed an erroneous description of risk.tak in the DISCUSSION section.

Minor wordsmithing to save a line here and there, where there was only one word in the last line of a paragraph, to keep the length to 12 pages.

<<knitr_setup, echo=F, results='hide', cache=F>>=
library(knitr)
opts_chunk$set(fig.align = "center")
@

@@

In our model, traders bet on global temperature anomalies six years in the future.
During the six-year period, traders buy and sell futures.
Every year, traders update their models and forecast of future temperatures based on newly available data.
At the end of each six-year period, winners collect gains and traders revise beliefs about climate models, based on their ideology and the beliefs of top earners in their social network.
In this section, we describe the models used to generate future temperature data, agents beliefs about those models, the market procedures, and the social network connecting agents.
We conclude with details on model dynamics and an overview of the model parameters we experimentally vary. A full Overview, Design concepts and Details (ODD) report on our model can be found on \href{https://github.com/JohnNay/predMarket}{the project website}.

@@

The higher the risk tolerance, the greater the range of prices at which a trader will buy and sell securities. This creates greater opportunities for traders to profit if their model is correct and to lose money if it is incorrect. This increased volatility puts more information in play, and we believe this is why greater risk taking enables traders to identify the correct model more quickly. We have observed a similar phenomenon in a very different context, where adding stochastic noise to player decisions in iterated games improves the accuracy with which machine-learning algorithms can identify the players' strategies \shortcite{Nay2015}.

@@

All code and data for the model is available at \href{https://github.com/JohnNay/predMarket}{github.com/JohnNay/predMarket}. This project is a computational test-bed for public policy design: our code can be extended to test the effects that trading strategies, cognitive models, future climate scenarios, and market designs have on the evolution of trader beliefs.

>>>>

<<knitr_setup, echo=F, results='hide', cache=F>>=
library(knitr)
opts_chunk$set(fig.align = "center", cache = FALSE)
@

@@

In our model, traders bet on global temperature anomalies six years in the future.
During the six-year period, traders buy and sell futures.
Every year, traders update their models and forecast of future temperatures based on newly available data.
At the end of each six-year period, winners collect gains and traders revise beliefs about climate models, based on their ideology and the beliefs of top earners in their social network.
In this section, we describe the models used to generate future temperature data, agents beliefs about those models, the market procedures, and the social network connecting agents.
We conclude with details on model dynamics and an overview of the model parameters we experimentally vary. The model code and a full \href{https://github.com/JohnNay/predMarket/blob/master/odd.pdf}{Overview, Design concepts and Details (ODD) specification} can be found on \href{https://github.com/JohnNay/predMarket}{the project website}.

@@

Traders with higher risk tolerance will price buy and sell orders more aggressively, so they will earn more (or lose less) on completed trades, but will have a greater risk of failing to complete trades. Among traders with the correct model of climate, those with higher risk tolerance  will earn more profit on completed trades (and their counterparties will lose more). A trader's wealth is an important source of information, and we believe this is why greater risk taking enables traders to identify the correct model more quickly. Additionally, the risk of failing to complete trades adds volatility, which also puts information in play. We have observed a similar phenomenon in a very different context, where adding stochastic noise to player decisions in iterated games improves the accuracy with which machine-learning algorithms can identify the players' strategies \shortcite{Nay2015}.

@@

All code and data for the model is available at \href{https://github.com/JohnNay/predMarket}{github.com/JohnNay/predMarket}. This project is a computational test-bed for public policy design: our code can be extended to test the effects of trading strategies, cognitive models, future climate scenarios, and market designs on the evolution of trader beliefs.
